\documentclass[a4paper,12pt]{article}

% Font configuration for Times New Roman
\usepackage{mathptmx}
\usepackage[T1]{fontenc}

% Page geometry settings (25mm top/bottom, 20mm left/right)
\usepackage[top=25mm, bottom=25mm, left=20mm, right=20mm]{geometry}

% Remove page numbers, headers, and footers
\pagestyle{empty}

% Optional packages for tables and graphics
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[natbibapa]{apacite}

% Custom command for run-in headings
\newcommand{\heading}[1]{%
  \noindent\textbf{#1}%
}

\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\begin{document}

% Top Matter
\begin{center}
    {\fontsize{13.4pt}{12pt}\selectfont 
    \textbf{You should Plugin your Telemed Ultrasound}\par}
    % \vspace{1em}
    {\fontsize{12pt}{10pt}\selectfont
    Pertti Palo$^{1}$, Co-author Full Name$^{2}$\par
    \vspace{0.25em}
    $^{1}$University of Alberta, Edmonton, Alberta, Canada\\
    $^{2}$Affiliation\par
    \vspace{0.25em}
    pertti.palo@taurlin.org, Author 2 email address\par
    \vspace{-0.75em}
    }
\end{center}

\heading{Introduction.}

\begin{itemize}
  \item \citep{Stone-GuideAnalyzingTongue-2005}
  \item Telemed devices are widely used these days. While the manual says to
  use mains power (connect the device's power source to a wall socket) it does
  not say why, and the device will work with just power from the USB-connection
  to a computer. We discovered by accident why this recommendation exists.
\end{itemize}


\heading{Purpose.}
This presentation provides a description of the consequences to data quality,
description of how to detect if old data has been compromised and a
recommendation for future data recording.


\heading{Method.}

\begin{itemize}
  \item PD \citep{Palo-MeasuringPrespeechArticulation-2019}
  \item DeepLabCut \citep{WrenchBalch-Tomes-EdgeMarkerlessPose-2022}
  \item 
\end{itemize}


\heading{Results.}

\begin{itemize}
  \item example of bad data in PD
  \item example of sneakily bad data in PD
  \item similar for splining/image quality
\end{itemize}

\heading{Conclusion.}
The conclusion for new data is simple: Plug the ultrasound machine into mains
power when ever possible and if you need to run it with only USB power, make a
note of that in your recording metadata / laboratory journal. 

For old data, if you do not know that the device was plugged in to mains
electricity,  

\setlength{\leftmargin}{1.5em}%
\setlength{\itemindent}{-1.5em}%
\setlength{\parsep}{0pt}%
\setlength{\itemsep}{0.2em}%

\heading{References.}
\renewcommand{\bibsection}{}
\renewcommand{\doiprefix}{}
\bibliographystyle{apacite}
\bibliography{science_combined}


% Custom environment for hanging indentation references
% \newenvironment{reflist}{%
%   \begin{list}{}{%
%     \setlength{\leftmargin}{1.5em}%
%     \setlength{\itemindent}{-1.5em}%
%     \setlength{\parsep}{0pt}%
%     \setlength{\itemsep}{0.2em}%
%   }
% }{%
%   \end{list}
% }
% \begin{reflist}
% \item Author, A. A. (2026). Title of reference. \textit{Journal Name}, Volume, Page range.
% \item Use a consistent format for references and inline citations.
% \end{reflist}

\end{document}
